---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# grepr

<!-- badges: start -->
<!-- badges: end -->

grepr aims to provide a similar functionality as the bash command `grep`,
but display the results as RStudio source markers

## Installation

You can install the developent version of grepr from GitHub with:

``` r
remotes::install_github("GregorDeCillia/grepr")
```

## Example

This package exposes one single function called `grepr`, which finds matches
based on a regular expression.

```{r}
library(grepr)
grepr(pattern = "message") %>% as.data.frame() %>% head(3)
```

If `grepr` is called in RStudio, the results are displayed as RStudio markers.

## Arguments

Argument           | Description
-------------------|------------------------------------------------------------
**pattern**        | a character string containing a regular expression
**dir**            | a directory from which the search is conducted. Defaults to the working directory.
**ignore_dotfiles**| should hidden files be searched as well? Defaults to `FALSE`
**file_pattern**   | a regular expression which can be used to exclude certain files from the search

## Umlauts

`grep_umlauts` is a wrapper around `grepr` which looks for umlauts via the 
`pattern` argument. It can be used with a flag `ignore_roxygen` to skip Rd
Files and roxygen comments.

Supported symbols: ÖÄÜöäü

```{r}
grep_umlauts(file_pattern = "README\\.Rmd") %>% as.data.frame()
```

The function `print_substitution_table()` can be used to suggest alternatives

```{r}
print_substitution_table()
```

