---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = FALSE
)
```

# grepr

<!-- badges: start -->
<!-- badges: end -->

grepr aims to provide a similar functionality as the bash command `grep`
and display the results as RStudio source markers

## Installation

You can install the developent version of grepr from GitHub with:

``` r
remotes::install_github("GregorDeCillia/grepr")
```

## Example

The function `grepr` can be used to find matches in files based on a regular
expression.

```{r}
library(grepr)
grepr("message")[5:9, ]
```

If `grepr` is called in RStudio, the results are displayed as
[RStudio source markers](https://rstudio.github.io/rstudioapi/reference/sourceMarkers.html).

## Arguments

Argument           | Description
-------------------|------------------------------------------------------------
**pattern**        | a character string containing a regular expression
**dir**            | a directory from which the search is conducted. Defaults to the working directory.
**ignore_dotfiles**| should hidden files be ignored? Defaults to `TRUE`
**file_pattern**   | a regular expression which can be used to exclude certain files from the search

## Umlauts

`grep_umlauts` is a wrapper around `grepr` which looks for umlauts via the 
`pattern` argument. It can be used with a flag `ignore_roxygen` to skip Rd
Files and roxygen comments.

Supported symbols: Ö, Ä, Ü, ö, ä, ü, ß

```{r}
grep_umlauts(file_pattern = "README\\.Rmd")
```

The function `print_substitution_table()` can be used to suggest alternatives

```{r}
print_substitution_table()
```

## Class methods

Calls to `grepr::grepr()` create objects of the class `grepr`. Those objects
can be used in the following ways.

* printing an object in an interactive console will display the matches with
  `rstudioapi::sourceMarkers()`
* printing an object in a RMarkdown file will render the matches with
  `knitr::kable()`
* the generic `as.data.frame()` converts the matches into a tidy `data.frame`
  that contains filenames, row numbers, colum numbers and lengths of the
  matches.
  
```{r}
grep_umlauts(file_pattern = "README\\.Rmd") %>% as.data.frame()
```

## Known Issues

* in RMarkdown documents with markdown output, square brackets (`[` and `]`)
  get escaped in a way that can affect the markup of `knit_print.grepr()`:
  https://github.com/rstudio/rmarkdown/issues/667
* double quotes (`"`) are displayed as fancy quotes (<code>&ldquo;</code>) in
  column `content`
* currently, there is no check if RStudio is running which might lead to errors
  in the print method in case another IDE or no IDE is used
  
## Possible improvements

* add `grep_package()` which respects the contents of `.gitignore` and
  `.Rbuildignore` by default
* ignore BLOBS and other problematic file types by default
* add `gsub_umlauts()` which applies the suggestions in
  `print_substitution_table()` automatically
